
\section{Introduction}
\label{sec:introduction}

Sweetie is a One-To-One app thought and designed to be the main communication and sharing
tool for a couple relationship. Every conversation, photo, images, to-do lists, localized messages and memory of the couple will pass through Sweetie. The idea was born from the need of an intimate and special place for the couple in our smartphone that is not satisfied by 'general purpose' platforms like WhatsApp and Facebook.

The application described in this paper is the first step in order to show a minimal product to potential investors. The main features built are:

\begin{itemize}
	\item Multiple chats based on the today's standard of messaging apps leader, WhatsApp and Telegram;
	\item Galleries that are containers of images grouped by both partners;
	\item Infos of Chat, Gallery and To-Do list, accessible from the menu of each, show the date of creation and, optional, the photo cover. Only for the galleries there is the optional placement, selectable through a Location Picker UI;
	\item To-Do lists managed by both, for any kind of topic, like grocery list, movies to watch, trips to plan;
	\item Geogift, are messages like a post-it, pictures or emoticons, geolocalized. The partner won't know about the gift until he/she will come exactly on that physical place e.g., a specific street address or store in the city. This thanks to the geofence, a virtual perimeter set on a real geographic area that should be monitored by a service. The simplest geofence to be created needs of center position, explicated by latitude and longitude, and the radius of circle area, setted in meters. When the boundary of geofence is crossed, the user is alerted by a push notification. This feature need to be enable manually in the settings activity;
	\item Maps to see, as a markers, the Geogifts sent or discovered and the galleries that have a photo cover and a location specified;
	\item Calendar where to easily visualize the own saved message (bookmarked).
\end{itemize}

We don't put so much effort into usability and accessibility that an Android app needed, for example our app lacks of a initial tutorial or a welcome page where the user is instructed with what he could do with Sweetie furthermore some important feature: image compression and a complete notifications service were not implemented, we preferred to invest the last works time to test our application in order to fix underhand bugs. The application is built and tested for Android Lollipop 5.1, Marshmallow 6.0 and Nougat 7.0, these version are almost the 70\% of the market and we think that when Sweetie will be release the percentage will increase\footnote{Data collected during a 7-day period ending on September 11, 2017 \url{https://developer.android.com/about/dashboards/index.html}}. 

The paper is organized as follows: section~\ref{sec:app-domain} describes how we analysis the domain of Sweetie and what are the entities that we manipulated for create the core business logic of the application. Section~\ref{sec:app-architecture} expose the app architecture, with merits and defects, and why we have done some choices. Section~\ref{sec:ext_api} show the list of external library that are used in order to support some feature of Sweetie. In section~\ref{sec:issues} we group all the major problematics that requires more effort and we explain the solution or workaround that we implements with some accepted trade-offs. Section~\ref{sec:futureworks}  show some important feature that our app has not yet implemented. Finally the section ~\ref{sec:conclusion} describes our considerations on the development of this project.
